\ProjectName{}: Data Imputation as a Query Optimization

### 2016-12-14 paper/examples.tex
paper: example query into lstlisting env, wrapped in figure and added ref

The analyst submits a query (\todo{ref to listing}) to ImputeDB which finds an optimized query
plan\footnote{The analyst specifies a relatively high value of $\alpha$, the quality
emphasis parameter, in order to receive a plan that does an expensive imputation step. See
Section~\ref{sec:cost-model} for more details.}. The resulting query plan
(Figure~\ref{fig:query-plan})
imputes missing values for \verb!acs.TEL! after states with high polling error have been
selected. This decision reduces the set of tuples that must be input into the imputation
algorithm to just those that are relevant to the query. Later, we show the algorithms that
the ImputeDB query optimizer uses in order to detect these opportunities and control the
tradeoffs between efficiency and imputation quality.

\begin{verbatim}
SELECT polling.ST, AVG(acs.TEL)
FROM polling, acs
WHERE polling.ST = acs.ST
  AND polling.ERROR > 50         -- 5 percentage points
GROUP BY polling.ST;
\end{verbatim}

>>>>

The analyst submits a query (Figure~\ref{fig:example-query}) to ImputeDB which finds an optimized query
plan\footnote{The analyst specifies a relatively high value of $\alpha$, the quality
emphasis parameter, in order to receive a plan that does an expensive imputation step. See
Section~\ref{sec:cost-model} for more details.}. The resulting query plan
(Figure~\ref{fig:query-plan})
imputes missing values for \verb!acs.TEL! after states with high polling error have been
selected. This decision reduces the set of tuples that must be input into the imputation
algorithm to just those that are relevant to the query. Later, we show the algorithms that
the ImputeDB query optimizer uses in order to detect these opportunities and control the
tradeoffs between efficiency and imputation quality. Finally, note that the optimizer doesn't
place any imputation operator for the \verb|acs.ST| column, as optimizer uses the histogram to
detect that there are no missing values there (as might be expected for a survey question that isn't
impacted by non-responses).

\begin{figure}
\begin{lstlisting}[language=SQL]
SELECT polling.ST, AVG(acs.TEL)
FROM polling, acs
WHERE polling.ST = acs.ST
  AND polling.ERROR > 50         -- 5 percentage points
GROUP BY polling.ST;
\end{lstlisting}
\caption{A typical analyst query on ACS data}
\label{fig:example-query}
\end{figure}

### 2016-12-14 paper/main.tex
Add example to paper
paper: example query into lstlisting env, wrapped in figure and added ref

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[activate={true,nocompatibility},final,kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[style=ieee]{biblatex}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{hyperref} % load after other packages
\addbibresource{references.bib}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[activate={true,nocompatibility},final,kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[style=ieee]{biblatex}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{hyperref} % load after other packages
\usepackage{graphicx} % includegraphics
\usepackage{listings} % code samples with syntax hl
\addbibresource{references.bib}

% listings settings
\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}; should come as last argument
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{red},    % comment style
  frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{gray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mauve},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
}
